\LARGE\textbf{Designing Studies and Evaluating Research Results:\\ Type M and Type S Errors for\\ Pearson Correlation Coefficient }

### 2021-09-03 Documents/Paper_main/Paper_main.Rnw
fix indexes in data plot

\maketitle
\thispagestyle{empty}
\begin{center}
\vfill
\textbf{Submitted to \textit{Meta-Psychology}. Click here to follow the fully transparent editorial process of this submission. Participate in open peer review by commenting through hypothes.is directly on this preprint.}
\vfill
\textbf{\large Author Note}
\end{center}
\orcidicon ORCiD\\
Giulia Bertoldo: \href{https://orcid.org/0000-0002-6960-3980}{0000-0002-6960-3980}\\
Claudio Zandonella Callegher:\href{https://orcid.org/0000-0001-7721-6318}{0000-0001-7721-6318}\\
Gianmarco Altoè: \href{https://orcid.org/0000-0003-1154-9528}{0000-0003-1154-9528}

@@

% added info peer revieew
\noindent \textit{Under peer review at Meta-Psychology. This is a revised version of the submitted paper. The editorial process, including decision letters and reviews, can be accessed at:}

@@

<<Data_plot_scenarios, eval = F>>=
conditions <- expand.grid(rho = c(.25, .50, .75),
                          n = c(3:20,seq(from=22, to=40, by=2),seq(from=45, to=100, by=5), seq(from=110, to=200, by=10),250,300,500))
conditions$B <- c(rep(7e5, 3),rep(5e4, 150))

@@

data_conditions_rho <- mapply(retro_r, conditions_rho$rho[1:12],conditions_rho$n[1:12],
                              B = conditions_rho$B[1:12], seed=2020)

>>>>

\maketitle
\thispagestyle{empty}
\begin{center}
\vfill
\textbf{In press at \textit{Meta-Psychology}. Click \href{http://tinyurl.com/mp-submissions}{here}  to follow the fully transparent editorial process of this submission. Participate in open peer review by commenting through hypothes.is directly on this preprint.}
\vfill
\textbf{\large Author Note}
\end{center}
\orcidicon ORCiD\\
Giulia Bertoldo: \href{https://orcid.org/0000-0002-6960-3980}{0000-0002-6960-3980}\\
Claudio Zandonella Callegher:\href{https://orcid.org/0000-0001-7721-6318}{0000-0001-7721-6318}\\
Gianmarco Altoè: \href{https://orcid.org/0000-0003-1154-9528}{0000-0003-1154-9528}

@@

% added info peer revieew
\noindent \textit{In press at Meta-Psychology. This is a revised version of the submitted paper. The editorial process, including decision letters and reviews, can be accessed at:}

@@

<<Data_plot_scenarios, eval = F>>=
conditions <- expand.grid(rho = c(.25, .50, .75),
                          n = c(3:20,seq(from=22, to=40, by=2),seq(from=45, to=100, by=5), seq(from=110, to=200, by=10),250,300,500))
conditions$B <- c(rep(7e5, 9),rep(5e4, 150))

@@

data_conditions_rho <- mapply(retro_r, conditions_rho$rho,conditions_rho$n,
                              B = conditions_rho$B, seed=2020)
